### 2017-05-13 paper/evaluation.tex
rq7 (best I can do for the time)

\begin{figure*}[t]  
\centering
\small
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T$ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{1.85x}{0.23\%} & \entry{3.36x}{3.1\%}\\%

@@

\bottomrule%
\end{tabular}
\caption{Speedup versus Flakiness (\subcolB). Configuration
  \emph{\Seq{}} denotes the comparison baseline, which runs tests
  sequentially.  Columns $T$ and $N$ indicate time and number of
  tests, respectively.  Other columns show speedup and percentage of
  failing tests in different configurations, compared to
  \emph{\Seq{}}.\Mar{Can you please add name of module for all subjects?}}
\label{tab:rq6-table}
\end{figure*}

@@

\Mar{estou aqui...}

Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
subject's name. Values are reported in average \Fix{LEMBRAR DE MOSTRAR
  VALORES DE DESVIO PADRAO!}.

@@

\Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
Possivelmente o slowdown se deve ao tempo de resposta do servico quando
a autentiticao falha}

\Fix{Elaborate results from efficiency}

\Fix{Elaborate results from flakiness}

\Fix{highlight special cases}

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQIssuesOne{}:~\emph{\Jbc{summarize findings...}}}
\end{minipage}
}
\end{center}

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive
%%  LocalWords:  linkbench priori

>>>>

\begin{figure*}[t]  
\centering
\small
\setlength{\tabcolsep}{2pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T$ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{1.85x}{0.23\%} & \entry{3.36x}{3.1\%}\\%

@@

\bottomrule%
\end{tabular}
\caption{Speedup versus Flakiness (\subcolB). Configuration
  \emph{\Seq{}} denotes the comparison baseline, which runs tests
  sequentially.  Columns $T$ and $N$ indicate time and number of
  tests, respectively.  Other columns show speedup and percentage of
  failing tests in different configurations, compared to
  \emph{\Seq{}}.}
\label{tab:rq6-table}
\end{figure*}

@@

Figure~\ref{tab:rq6-table} summarizes results ordered by subject's
name. Recall that we only executed one module for each subject.
Values are averaged across multiple executions.  We did not report
standard deviations as they are very small in all cases.  Considering
flakiness, results show that 0\% of flakiness have been reported in 26
of the 60 combinations analyzed (43\% of the total) and that for seven
of the ten projects 0\% flakiness was reported in at least one of the
configurations.  The projects with flakiness in all configurations
were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.
It is worth highlighting the unfortunate case of \CodeIn{Moquette},
which manifested more than 20\% flaky tests in every configuration.
Considering time, it is noticeable from the averages, perhaps as
expected, an increasing speedup from configuration
\emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and from
configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
  test suites of 70\% of the projects we analyzed could be run in
  parallel without manifesting any flaky tests.  In some of these
  cases, speedups were significant, ranging from 1x to 28.8x.}
\end{minipage}
}
\end{center}

@@

%% \Jbc{Lembrar que investigar o slowdown de Dataflow... os logs indicam que varios
%% dos testes que quebraram tentavam fazer uma autenticacao em algum servico.
%% Possivelmente o slowdown se deve ao tempo de resposta do servico quando
%% a autentiticao falha}

%% \Fix{Elaborate results from efficiency}

%% \Fix{Elaborate results from flakiness}

%% \Fix{highlight special cases}

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs
